---
title: "Determining the most effective Test for Liver disease that might be caused by excessive Alcohol Consumption"
author: "demola"
date: "12/7/2021"
output: html_document
---

```{r}
df <- read.csv("~/Downloads/discover_pattern.csv")
df
```
Renaming the Columns
```{r}
names(df) <- c('MCV', 'Alkphos','Sgpt', 'Sgot', 'Gammagt', 'Drinks')
df
```

Dropping Column Seven because it will have no effect on the analysis
Dropping some columns - The data points were too much and they were messing up the 3d Heatmap hence, I reduced the data-points by 
dropping 294 Rows
```{r}
new <- df[c(1,2,3,4,5,6)]
new1 <- new[-c(50:343), ]
print(new1)
```
Checking the Descrptive Statistics of the DataSet Using the Describe() Function
```{r}
describe(new1)
```

Checking for the Summary of the DataSet using the summary() Function
```{r}
print(new1)
summary(new1)
```
Normalizing the Variable to make them more comparable
```{r}
nw <- normalize(new1)
nw
```

This Code displays the 3dbarchart but the plot_gg function is absent in the ggplot library. This is a software error, and it is confirmed after doing my research online.
```{r}
new2 = ggplot(nw) + 
  geom_point(aes(x=MCV,color=cyl,y=Drinks),size=2) +
  scale_color_continuous(limits=c(0,8)) +
  ggtitle("mtcars: Displacement vs mpg vs # of cylinders") +
  theme(title = element_text(size=8),
        text = element_text(size=12)) 
plot_gg(new2, height=3, width=3.5, multicore=TRUE, pointcontract = 0.7, soliddepth=-200)
```

Checking for collinearity between the columns and the rows Using an Interactive Heat-map

```{r}
heatmaply(
  nw,
  colors = viridis(n = 256,  option = "magma"),
  k_col = 2, 
  k_row = 2
)
```
This interactive Heatmap displays the correlation of values using the colors from magma. 
variables with higher collinearity has the Yellow Color while Variables with the Lower collinearity displays the Black 
Color

Also, The heatmap clusters Rows that are highy similar. 









